Designing and modeling a browser-based distributed evolutionary computation systems

### 2015-04-01 modeling-volunteer-computing-gecco.tex
Adds loggly description

During and after the experiment, the data can be collected from one of
the logs: the log file (if the PaaS allows writing to the filesystem,
which is not the case in Heroku) or to online logging services such as
Loggly, which is the one we are using.

As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in the GitHub
repository \url{https://github.com/JJ/splash-volunteer}. 
will be analyzed in the next section.

>>>>

During and after the experiment, the data can be collected from one of
the logs: the log file (if the PaaS allows writing to the filesystem,
which is not the case in Heroku) or to online logging services such as
Loggly, which is the one we are using. Loggly was chosen for its
easiness and support from the {\tt winston} logging library; however,
it is only free for a month, so a more sustainable alternative (read:
free) will have to be sought in the future. Other online logging
services have a free tier that can be used for ever; however, its
support and facilities are not so good. Choosing a good logging
service for experiments in open science is an open issue but it is
outside the scope of this paper. It will have to be left for future
work. 
% Include loggly graphs here.
As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in the GitHub
repository \url{https://github.com/JJ/splash-volunteer}. 
will be analyzed in the next section.
